Clarify RQ and Design

### 2024-10-31 clarifyRQsandDesign.Rmd
restructurecommit2
jochemfeedbackrqs

@@

aka. looking at Sociology Department and extent of homphily in there \
and comparing it with Political Science Department and extent of homophily in there.

@@

    -   Isn't that the same question as RQ1a then?

@@

    -   Did not intent to look at changes over time. this would change things up.

-   Or should it be about the prestige variable in some way? \
    e.g. whether we observe gender homophily within collaboration networks of high prestige scholars and within collaboration networks of lower prestige scholars

@@

@@

# Design

# Project parts

## Research Design

-   Clarify Research Questions

-   Clarify design to answer this question

-   Clarify which data is needed in the design

## Steps to analysis

-   Step 1: Define data

-   Step 2: Create effects structure

-   Step 3: Get initial description

-   Step 4: Specify model

-   Step 5: Estimate model

-   Step 6: Goodness of Fit

## Report writing

-   Introduction

-   Theory

-   Data & Methods

-   Results

-   Discussion & Conclusion

>>>>

*yes perfect. just a descriptive question at the macro-level. keep it as it is.*

@@

aka. looking at Sociology Department and extent of homphily in there\
and comparing it with Political Science Department and extent of homophily in there.

*also okay. still a descriptive question at the macro-level. keep it as it is.*

@@

    -   Isn't that the same question as RQ1a then?
    -   *yes and no. ;-)  this is your hypothesis for your RSiena models. whether within a dyad men tend to (or 'prefer') work with men and women with women, (controlled for structural network effects). \
        I hope that you understand that this **dyadic preferences does not necessarily translates to your macro-outcome** (because of all structural effects possibly at play and other covariate-effects).*

@@

    -   Did not intent to look at changes over time. this would change things up.
    -   *okay, simply do not do this then.*

-   Or should it be about the prestige variable in some way?\
    e.g. whether we observe gender homophily within collaboration networks of high prestige scholars and within collaboration networks of lower prestige scholars

@@

-   *keep it simple! completely agree.*

    *so far we simply have a descriptive question on gender homophily at the network-level (RQ1) and one at the dyad-level (after controlling for structural network effects and covariate-effects) (RQ2).*

@@

*Try to reformulate this to your RSiena model and not at your macro-level. I let you struggle a little bit on this last one okay. \
But the idea is fine; whether prestige (of ego/alter/dyad) impacts gender homophily in some way.*

*Thus **start with your descriptives and modelling \
**and rephrase RQ3 later.*

*try to **plot asap in the process**. \
and update plots after descriptives and multivariate analyses along the way. it is an iterative process.*
